---
title: "Tufte in R"
author: "許sir"
---

```{}
本文的原始網址如下 http://motioninsocial.com/tufte/

耶魯大學 Edward Tufte 教授可說是當代視覺化最有名的人物，其四本視覺化相關著作可說是視覺化聖經；然而，他做過的圖表都是常人能輕鬆重製的嗎？沒問題，來參考「Tufte in R 」專案吧！這個專案期望能把 Tufte 設計的各種圖表利用 R 完整重製一遍，目前已有 25 個圖表，全都附有程式碼供參考。

學視覺化，就從大師開始抄起！
```

### **[Requirements]**
```{}
install.packages(c("CarletonStats", "devtools", "fmsb", "ggplot2", "ggthemes", 
                   "latticeExtra", "MASS", "PerformanceAnalytics", "psych", 
                   "plyr", "proto", "RCurl", "reshape", "reshape2"))
```


```{r}
setwd("D:/Rdata Practice/Tufte in R")
```

### **[Part 1].Minimal line plot **

#### **1. Minimal line plot in base graphics**
```{r message=FALSE, warning=FALSE}
x <- 1967:1977
y <- c(0.5,1.8,4.6,5.3,5.3,5.7,5.4,5,5.5,6,5)
pdf(width=10, height=6)
plot(y ~ x, axes=F, xlab="", ylab="", pch=16, type="b")
axis(1, at=x, label=x, tick=F, family="serif")
axis(2, at=seq(1,6,1), label=sprintf("$%s", seq(300,400,20)), tick=F, las=2, family="serif")
abline(h=6,lty=2)
abline(h=5,lty=2)
text(max(x), min(y)*2.5,"Per capita\nbudget expanditures\nin constant dollars", adj=1, 
     family="serif")
text(max(x), max(y)/1.08, labels="5%", family="serif")
dev.off()
```

#### **2. Minimal line plot in lattice**
```{r message=FALSE, warning=FALSE}
library(lattice)
x <- 1967:1977
y <- c(0.5,1.8,4.6,5.3,5.3,5.7,5.4,5,5.5,6,5)
xyplot(y~x, xlab="", ylab="", pch=16, col=1, border = "transparent", type="o",
       abline=list(h = c(max(y),max(y)-1), lty = 2),
       scales=list(x=list(at=x,labels=x, fontfamily="serif", cex=1),
                   y=list(at=seq(1,6,1), fontfamily="serif", cex=1,
                          label=sprintf("$%s",seq(300,400,20)))),
       par.settings = list(axis.line = list(col = "transparent"), dot.line=list(lwd=0)),
       axis = function(side, line.col = "black", ...) {
         if(side %in% c("left","bottom")) {axis.default(side = side, line.col = "black", ...)}})
ltext(current.panel.limits()$xlim[2]/1.1, adj=1, fontfamily="serif", 
      current.panel.limits()$ylim[1]/1.3, cex=1,
      "Per capita\nbudget expandures\nin constant dollars")
ltext(current.panel.limits()$xlim[2]/1.1, adj=1, fontfamily="serif", 
      current.panel.limits()$ylim[1]/5.5, cex=1, "5%")
```

#### **3. Minimal line plot in ggplot2**
```{r message=FALSE, warning=FALSE}
library(ggplot2)
library(ggthemes)
x <- 1967:1977
y <- c(0.5,1.8,4.6,5.3,5.3,5.7,5.4,5,5.5,6,5)
d <- data.frame(x, y)
ggplot(d, aes(x,y)) + geom_line() + geom_point(size=3) + theme_tufte(base_size = 15) +
  theme(axis.title=element_blank()) + geom_hline(yintercept = c(5,6), lty=2) + 
  scale_y_continuous(breaks=seq(1, 6, 1), label=sprintf("$%s",seq(300,400,20))) + 
  scale_x_continuous(breaks=x,label=x) +
  annotate("text", x = c(1977,1977.2), y = c(1.5,5.5), adj=1,  family="serif",
           label = c("Per capita\nbudget expandures\nin constant dollars", "5%"))
```

### **[Part 2].Range-frame (or quartile-frame) scatterplot  **

#### **4. Range frame plot in base graphics**
```{r message=FALSE, warning=FALSE}
x <- mtcars$wt
y <- mtcars$mpg
plot(x, y, main="", axes=FALSE, pch=16, cex=0.8, family="serif",
xlab="Car weight (lb/1000)", ylab="Miles per gallon of fuel")
axis(1,at=summary(x),labels=round(summary(x),1), tick=F, family="serif")
axis(2,at=summary(y),labels=round(summary(y),1), tick=F, las=2, family="serif")
```

#### **5. Range frame plot in base graphics with fancyaxis**
```{r message=FALSE, warning=FALSE}
library(devtools)
source_url("https://raw.githubusercontent.com/sjmurdoch/fancyaxis/master/fancyaxis.R")
x <- mtcars$wt
y <- mtcars$mpg
plot(x, y, main="", axes=FALSE, pch=16, cex=0.8,
     xlab="Car weight (lb/1000)", ylab="Miles per gallon of fuel")
fancyaxis(1, summary(x), digits=1)
fancyaxis(2, summary(y), digits=1)
```

#### **6. Range frame plot in lattice**
```{r message=FALSE, warning=FALSE}
library(lattice)
x <- mtcars$wt
y <- mtcars$mpg
xyplot(y ~ x, mtcars, col=1, pch=16, fontfamily="serif",
xlab="Car weight (lb/1000)", ylab="Miles per gallon of fuel",
par.settings = list(axis.line = list(col="transparent"),
par.xlab.text=list(fontfamily="serif"),
par.ylab.text=list(fontfamily="serif")),
scales = list(x=list(at=summary(mtcars$wt),labels=round(summary(mtcars$wt),1),
fontfamily="serif"),
y=list(at=summary(mtcars$mpg),labels=round(summary(mtcars$mpg),1),
fontfamily="serif")),
axis = function(side, line.col = "black", ...) {
if(side %in% c("left","bottom")) {axis.default(side = side, line.col = "black", ...)}})
```

#### **7. Range-frame plot in ggplot2**
```{r message=FALSE, warning=FALSE}
library(ggplot2)
library(ggthemes)
ggplot(mtcars, aes(wt, mpg)) + geom_point() + geom_rangeframe() + theme_tufte() +
xlab("Car weight (lb/1000)") + ylab("Miles per gallon of fuel") + 
theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=1.5))
```

### **[Part 3].Dot-dash (or rug) scatterplot  **

#### **8. Dot-dash plot in base graphics with fancyaxis**
```{r message=FALSE, warning=FALSE}
library(devtools)
source_url("https://raw.githubusercontent.com/sjmurdoch/fancyaxis/master/fancyaxis.R")
x <- mtcars$wt
y <- mtcars$mpg
plot(x, y, main="", axes=FALSE, pch=16, cex=0.8,
xlab="Car weight (lb/1000)", ylab="Miles per gallon of fuel", 
xlim=c(min(x)-0.2, max(x)+0.2),
ylim=c(min(y)-1.5, max(y)+1.5))
axis(1, tick=F)
axis(2, tick=F, las=2)
minimalrug(x, side=1, line=-0.8)
minimalrug(y, side=2, line=-0.8)
```

#### **9. Dot-dash plot in lattice**
```{r message=FALSE, warning=FALSE}
library(lattice)
x <- mtcars$wt
y <- mtcars$mpg
xyplot(y ~ x, xlab="Car weight (lb/1000)", ylab="Miles per gallon of fuel",
par.settings = list(axis.line = list(col="transparent")),
panel = function(x, y,...) { 
panel.xyplot(x, y, col=1, pch=16)
panel.rug(x, y, col=1, x.units = rep("snpc", 2), y.units = rep("snpc", 2), ...)})
```

#### **10. Dot-dash plot in ggplot2**
```{r message=FALSE, warning=FALSE}
library(ggplot2)
library(ggthemes)
ggplot(mtcars, aes(wt, mpg)) + geom_point() + geom_rug() + theme_tufte(ticks=F) + 
  xlab("Car weight (lb/1000)") + ylab("Miles per gallon of fuel") + 
  theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=1))
```

### **[Part 4].Minimal boxplot **

#### **11. Minimal boxplot in base graphics**
```{r message=FALSE, warning=FALSE}
x <- quakes$mag
y <- quakes$stations
boxplot(y ~ x, main = "", axes = FALSE, xlab=" ", ylab=" ",
pars = list(boxcol = "transparent", medlty = "blank", medpch=16, whisklty = c(1, 1),
medcex = 0.7,  outcex = 0, staplelty = "blank"))
axis(1, at=1:length(unique(x)), label=sort(unique(x)), tick=F, family="serif")
axis(2, las=2, tick=F, family="serif")
text(min(x)/3, max(y)/1.1, pos = 4, family="serif",
"Number of stations \nreporting Richter Magnitude\nof Fiji earthquakes (n=1000)")
```

#### **12. Minimal boxplot in base graphics with chart.Boxplot**
```{r message=FALSE, warning=FALSE}
library(PerformanceAnalytics)
library(psych)
d <- msq[,80:84]
chart.Boxplot(d, main = "", xlab="average personality rating (based on n=3896)", ylab="", 
element.color = "transparent", as.Tufte=TRUE)
```

#### **13. Minimal boxplot in lattice**
```{r message=FALSE, warning=FALSE}
x <- quakes$mag
y <- quakes$stations
bwplot(y ~ x, horizontal=F, xlab="", ylab="", do.out = FALSE, box.ratio = 0,
scales=list(x=list(labels=sort(unique(x)), fontfamily="serif"),
y=list(fontfamily="serif")),
par.settings = list(axis.line = list(col = "transparent"), box.umbrella=list(lty=1, col= 1),
box.dot=list(col= 1), box.rectangle = list(col= c("transparent"))))
ltext(current.panel.limits()$xlim[1]+250, adj=1,
current.panel.limits()$ylim[2]+50, fontfamily="serif",
"Number of stations \nreporting Richter Magnitude\nof Fiji earthquakes (n=1000)")
```

#### **14. Minimal boxplot in ggplot2**
```{r message=FALSE, warning=FALSE}
library(ggplot2)
library(ggthemes)
ggplot(quakes, aes(factor(mag),stations)) + theme_tufte() +
geom_tufteboxplot(outlier.colour="transparent") + theme(axis.title=element_blank()) +
annotate("text", x = 8, y = 120, adj=1,  family="serif",
label = c("Number of stations \nreporting Richter Magnitude\nof Fiji earthquakes (n=1000)"))
```

### **[Part 5].Minimal barchart  **

#### **15. Minimal barchart in base graphics**
```{r message=FALSE, warning=FALSE}
library(psych)
d <- colMeans(msq[,c(2,7,34,36,42,43,46,55,68)], na.rm = T)*10
barplot(d, xaxt="n", yaxt="n", ylab="", border=F, width=c(.35), space=1.8)
axis(1, at=(1:length(d))-.26, labels=names(d), tick=F, family="serif")
axis(2, at=seq(1, 5, 1), las=2, tick=F, family="serif")
abline(h=seq(1, 5, 1), col="white", lwd=3)
abline(h=0, col="gray", lwd=2)
text(min(d)/2, max(d)/1.2, pos = 4, family="serif",
"Average scores\non negative emotion traits\nfrom 3896 participants\n(Watson et al., 1988)")
```

#### **16. Minimal barchart in lattice**
```{r message=FALSE, warning=FALSE}
library(lattice)
library(psych)
d <- colMeans(msq[,c(2,7,34,36,42,43,46,55,68)],na.rm = T)*10
barchart(sort(d), xlab="", ylab="", col = "grey", origin=1,  
border = "transparent", box.ratio=0.5, 
panel = function(x,y,...) {
panel.barchart(x,y,...)
panel.abline(v=seq(1,6,1), col="white", lwd=3)},
par.settings = list(axis.line = list(col = "transparent")))
ltext(current.panel.limits()$xlim[2]-50, adj=1,  
current.panel.limits()$ylim[1]-100,
"Average scores\non negative emotion traits\nfrom 3896 participants\n(Watson et al., 1988)")
```

#### **17. Minimal barchart in ggplot2**
```{r message=FALSE, warning=FALSE}
library(ggplot2)
library(ggthemes)
library(psych)
library(reshape2)
d <- melt(colMeans(msq[,c(2,7,34,36,42,43,46,55,68)],na.rm = T)*10)
d$trait <- rownames(d)
ggplot(d, aes(x=trait, y=value)) + theme_tufte(base_size=14, ticks=F) +
  geom_bar(width=0.25, fill="gray", stat = "identity") +  theme(axis.title=element_blank()) +
  scale_y_continuous(breaks=seq(1, 5, 1)) + 
  geom_hline(yintercept=seq(1, 5, 1), col="white", lwd=1) +
  annotate("text", x = 3.5, y = 5, adj=1,  family="serif",
label = c("Average scores\non negative emotion traits
          from 3896 participants\n(Watson et al., 1988)"))
```

### **[Part 6].Slopegraph **

#### **18. Slopegraph in base graphics**
```{}
From existing slopegraph functions for base graphics, the most promising one comes from Thomas Leeper. Its far from perfect, as labels don’t align nicely, but you have some control over a number of parametrs. For example, you can increase distance between labels using argument binval.
```

```{r message=FALSE, warning=FALSE}
library(devtools)
library(RCurl)
source_url("https://raw.githubusercontent.com/leeper/slopegraph/master/R/slopegraph.r")
d <- read.csv(text = getURL("https://raw.githubusercontent.com/jkeirstead/r-slopegraph/master/cancer_survival_rates.csv"))
df <- reshape(d, timevar = "year", idvar = c("group"), direction = "wide")
rownames(df) <- df$group; df <- round(df[,-1],0)
slopegraph(df, col.line='gray', xlim = c(-1, ncol(df)+2), binval = 2,
           labels=c("5 years", "10 years", "15 years", "20 years"),
           col.xaxt="transparent", main="")
```

#### **19. Slopegraph in lattice (in preparation)**

#### **20. Slopegraph in ggplot2**
```{}
As with base graphics, there are also problems with ggplot2 functions for making slopegraphs. The one from James Keirstead’s is the most promising but the main issue is with the value change from left to right side. As you see, some higher values display above lower values on the right side of graph. This can be adjusted with min.space in build_slopegraph but than you are likely to end up with overlapping labels.
```

```{r message=FALSE, warning=FALSE}
library(ggplot2)
library(ggthemes)
library(devtools)
library(RCurl)
library(plyr)
source_url("https://raw.githubusercontent.com/jkeirstead/r-slopegraph/master/slopegraph.r")
d <- read.csv(text = getURL("https://raw.githubusercontent.com/jkeirstead/r-slopegraph/master/cancer_survival_rates.csv"))
df <- build_slopegraph(d, x="year", y="value", group="group", method="tufte", min.space=0.04)
df <- transform(df, x=factor(x, levels=c(5,10,15,20), 
                             labels=c("5 years","10 years","15 years","20 years")), y=round(y))
plot_slopegraph(df) + labs(title="Estimates of % survival rates") +
  theme_tufte(base_size=16, ticks=F) + theme(axis.title=element_blank())
```

### **[Part 7].Sparklines  **
```{}
Sparklines in base graphics use some elements of functions from YaleToolkit developed by John Emerson and Walton Green. In particular, it’s a result of mine and Ben’s hacking of YaleToolkit functions on Stackoverflow. I’ve use a simple loop that takes a number of columns in a data set and creates as much sparklines as there are columns. In the same manner I use mfrow parameter in par() function to set the number of rows to a number of columns in data frame.
```


#### **21. Sparklines in base graphics**
```{r message=FALSE, warning=FALSE}
library(RCurl)
dd <- read.csv(text = getURL("https://gist.githubusercontent.com/GeekOnAcid/da022affd36310c96cd4/raw/9c2ac2b033979fcf14a8d9b2e3e390a4bcc6f0e3/us_nr_of_crimes_1960_2014.csv"))
d <- dd[,c(2:11)]
pdf("sparklines_base_multiple_ten.pdf", height=10, width=6)
par(mfrow=c(ncol(d),1), mar=c(1,0,0,8), oma=c(4,1,4,4))
for (i in 1:ncol(d)){
  plot(d[,i], lwd=0.5, axes=F, ylab="", xlab="", main="", type="l", new=F)
  axis(4, at=d[nrow(d),i], labels=round(d[nrow(d),i]), tick=F, las=1, line=-1.5, 
       family="serif", cex.axis=1.2)
  axis(4, at=d[nrow(d),i], labels=names(d[i]), tick=F, line=1.5, 
       family="serif", cex.axis=1.4, las=1)
  text(which.max(d[,i]), max(d[,i]), labels=round(max(d[,i]),0), 
       family="serif", cex=1.2, adj=c(0.5,3))
  text(which.min(d[,i]), min(d[,i]), labels=round(min(d[,i]),0), 
       family="serif", cex=1.2, adj=c(0.5,-2.5))
  ymin <- min(d[,i]); tmin <- which.min(d[,i]); ymax<-max(d[,i]); tmax<-which.max(d[,i]);
  points(x=c(tmin,tmax), y=c(ymin,ymax), pch=19, col=c("red","blue"), cex=1)
  rect(0, summary(d[,i])[2], nrow(d), summary(d[,i])[4], border=0, 
       col = rgb(190, 190, 190, alpha=90, maxColorValue=255))}
axis(1, at=1:nrow(dd), labels=dd$Year, pos=c(-5), tick=F, family="serif", cex.axis=1.4)
dev.off()
```

#### **22. Sparklines in lattice**
```{}
You have much better control over the location and size of sparklines when you use lattice. The only problem are right-side labels for which you have to use grid library in order to ‘hack’ the view parameters with functions pushViewport() and popViewport(). You can learn more about this in an extensive collection of grid vignettes. I still didn’t figure out how to do semi-transparent quantile area that Tufte uses in his examples - its work in progress.
```

```{r message=FALSE, warning=FALSE}
library(lattice)
library(latticeExtra)
library(grid)
library(reshape)
library(RCurl)
dd <- read.csv(text = getURL("https://gist.githubusercontent.com/GeekOnAcid/da022affd36310c96cd4/raw/9c2ac2b033979fcf14a8d9b2e3e390a4bcc6f0e3/us_nr_of_crimes_1960_2014.csv"))
d <- melt(dd, id="Year")
names(d)[1] <- "time"
pdf("sparklines_lattice_multiple_ten.pdf", height=10, width=8)
xyplot(value~time | variable, d, xlab="", ylab="", strip=F, lwd=0.7, col=1, type="l", 
       layout=c(1,length(unique(d$variable))), between = list(y = 1),
       scales=list(y=list(at=NULL, relation="free"), x=list(fontfamily="serif")), 
       par.settings = list(axis.line = list(col = "transparent"),
                           layout.widths=list(right.padding=20, left.padding=-5)),
       panel = function(x, y, ...) {
         panel.xyplot(x, y, ...)
         pushViewport(viewport(xscale=current.viewport()$xscale-5, 
                               yscale=current.viewport()$yscale, clip="off"))
         panel.text(x=tail(x,n=1), y=tail(y,n=1), labels=levels(d$variable)[panel.number()], 
                    fontfamily="serif", pos=4)
         popViewport()
         panel.text(x=x[which.max(y)], y=max(y), labels=round(max(y),0), cex=0.8,
                    fontfamily="serif",adj=c(0.5,2.5))
         panel.text(x=x[which.min(y)], y=min(y), labels=round(min(y),0), cex=0.8,
                    fontfamily="serif",adj=c(0.5,-1.5))
         panel.text(x=tail(x,n=1), y=tail(y,n=1), labels=round(tail(y,n=1),0), cex=0.8,
                    fontfamily="serif", pos=4)
         panel.points(x[which.max(y)], max(y),  pch=16, cex=1)
         panel.points(x[which.min(y)], min(y),  pch=16, cex=1, col="red")})
dev.off()
```

#### **23. Sparklines in ggplot2**
```{r message=FALSE, warning=FALSE}
library(ggplot2)
library(ggthemes)
library(dplyr)
library(reshape)
library(RCurl)
dd <- read.csv(text = getURL("https://gist.githubusercontent.com/GeekOnAcid/da022affd36310c96cd4/raw/9c2ac2b033979fcf14a8d9b2e3e390a4bcc6f0e3/us_nr_of_crimes_1960_2014.csv"))
d <- melt(dd, id="Year")
names(d) <- c("Year","Crime.Type","Crime.Rate")
d$Crime.Rate <- round(d$Crime.Rate,0)
mins <- group_by(d, Crime.Type) %>% slice(which.min(Crime.Rate))
maxs <- group_by(d, Crime.Type) %>% slice(which.max(Crime.Rate))
ends <- group_by(d, Crime.Type) %>% filter(Year == max(Year))
quarts <- d %>% group_by(Crime.Type) %>%
  summarize(quart1 = quantile(Crime.Rate, 0.25),
            quart2 = quantile(Crime.Rate, 0.75)) %>%
  right_join(d)
pdf("sparklines_ggplot_multiple_ten.pdf", height=10, width=8)
ggplot(d, aes(x=Year, y=Crime.Rate)) + 
  facet_grid(Crime.Type ~ ., scales = "free_y") + 
  geom_ribbon(data = quarts, aes(ymin = quart1, max = quart2), fill = 'grey90') +
  geom_line(size=0.3) +
  geom_point(data = mins, col = 'red') +
  geom_point(data = maxs, col = 'blue') +
  geom_text(data = mins, aes(label = Crime.Rate), vjust = -1) +
  geom_text(data = maxs, aes(label = Crime.Rate), vjust = 2.5) +
  geom_text(data = ends, aes(label = Crime.Rate), hjust = 0, nudge_x = 1) +
  geom_text(data = ends, aes(label = Crime.Type), hjust = 0, nudge_x = 5) +
  expand_limits(x = max(d$Year) + (0.25 * (max(d$Year) - min(d$Year)))) +
  scale_x_continuous(breaks = seq(1960, 2010, 10)) +
  scale_y_continuous(expand = c(0.1, 0)) +
  theme_tufte(base_size = 15, base_family = "Helvetica") +
  theme(axis.title=element_blank(), axis.text.y = element_blank(), 
        axis.ticks = element_blank(), strip.text = element_blank())
dev.off()
```

### **[Part 8].Stem-and-leaf display   **
```{}
Stem-and-leaf display is not exactly a ‘Tuftesque’ solution as it invented in the beginning of 20 century but was only popularised in 1980s by John Tukey. A stem-and-leaf display is a display for presenting quantitative data in a graphical format, similar to a histogram, to assist in visualizing the shape of a distribution. Stem-and-leaf plot is the only visualisation in this collection thats printed in the console in R rather than being processed with any graphical system.
```

#### **24. Stem-and-leaf display in console with base graphics**
```{r message=FALSE, warning=FALSE}
stem(faithful$eruptions)
```

#### **25. Stem-and-leaf display in console with CarletonStats**
```{r message=FALSE, warning=FALSE}
library(CarletonStats)
library(MASS)
stemPlot(birthwt$bwt, birthwt$smoke, varname="infant birth weight (in grams)",
         grpvarname="whether mother smoked during pregnancy (1) or not (0)")
```

#### **26. SStem-and-leaf display in base graphics with fmsb**
```{r message=FALSE, warning=FALSE}
library(fmsb)
gstem(faithful$eruptions)
```

